Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-19 checking-executions.tex
modify

TODO UPDATE THE NOTATIONS IN THIS EXAMPLE
Let us briefly explain the idea of proving this property when $\mathsf{MatchedMaxPriority}$ holds with an example. Given a data-differentiated concurrent execution $e \sqsubseteq u \cdot \textit{put}(x,p) \cdot v \cdot \textit{rm}(x) \cdot w \in \textit{MS}(\textit{PQ}_1)$ with witness $x$ and assume that $e \setminus x \sqsubseteq l' \in \textit{PQ}$, as shown in \figurename~\ref{fig:concurrent execution for EPQ1} (a), we explicitly construct a sequence $l''= l''_1 \cdot \textit{put}(x,p) \cdot l''_2 \cdot \textit{rm}(x) \cdot l''_3$ and prove that $e \sqsubseteq l'' \in \textit{PQ}$. In this example, $p_1 \prec p$, $p_1 \prec p_2$, $u=\epsilon$, $w$ contains $\textit{rm}(z_2), \textit{put}(x_3,p_2), \textit{rm}(z_1)$ (emphasize by $\textit{rm}(z_2)-w$), and the remanning operations are in $v$. We also explicitly draw the linearization points according to $l'$. We construct $l''$ as follows, and this method does not rely on the locations of linearization points of $l'$ and operations of $x$. Here we implicitly mix operation $o$ (when $\textit{call}_o(m,a)$, $\textit{ret}_o(m,b)$ in $e$) with $m(a,b)$.

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] Let $p$-comparable operations (resp., $p$-incomparable operations) be the set of operations with items whose priority is comparable with $p$ (resp., incomparable with $p$). It seems that we can construct $l''_1$, $l''_2$ and $l''_3$ as the projection of $l'$ into operations of $u$, $v$ and $w$, respectively. However, this is incorrect, since $\textit{PQ}_1$ has no restriction to $p$-incomparable operations operations in $u \cdot v$, and thus, there is no guarantee that the projection of $l'$ into $p$-incomparable operations operations in $u \cdot v$ being correct. In this example, such projection is $\textit{put}(z_1,p_3) \cdot \textit{rm}(z_2)$ and is incorrect.

@@

\item[-] The first step is to define $W'$. The $p$-comparable operations in $W'$ is same as that in $w$. To obtain $p$-incomparable operations in $W'$, we try to find a $p$-incomparable operation $o$ which either happens before some $p$-comparable operations in $w$, or with linearization points after $\textit{rm}(x)$. Then, we put $o$ and all $p$-incomparable operations after $o$ in $l'$ into $W'$ (emphasized by boxes in example). In this example, $o$ is $\textit{rm}(z_1)$, and $W'$ contains $\textit{put}(x_3,p)$, $\textit{rm}(z_1)$ and $\textit{rm}(z_2)$. We use boxes to emphasize they are put into $W'$.

>>>>

TODO UPDATE THE NOTATIONS IN THIS EXAMPLE

Let us briefly explain the idea of proving this property when $\mathsf{MatchedMaxPriority}$ holds with an example. Assume $e \sqsubseteq l=u \cdot \textit{put}(x,p) \cdot v \cdot \textit{rm}(x) \cdot w$, $\mathsf{MatchedMaxPriority}(l,x)$ holds, and $e \setminus x \sqsubseteq l' \in \textit{PQ}$, as shown in \figurename~\ref{fig:concurrent execution for EPQ1} (a), we explicitly construct a sequence $l''= l''_1 \cdot \textit{put}(x,p) \cdot l''_2 \cdot \textit{rm}(x) \cdot l''_3$ and prove that $e \sqsubseteq l'' \in \textit{PQ}$. In this example, $p_1 \prec p$, $p_1 \prec p_2$, $u=\epsilon$, $w$ contains $\textit{rm}(z_2), \textit{put}(x_3,p_2), \textit{rm}(z_1)$ (emphasize by $\textit{rm}(z_2)-w$), and the remanning operations are in $v$. We also explicitly draw the linearization points according to $l'$. We construct $l''$ as follows, and this method does not rely on the locations of linearization points of $l'$ and operations of $x$. Here we implicitly mix operation $o$ (when $\textit{call}_o(m,a)$, $\textit{ret}_o(m,b)$ in $e$) with $m(a,b)$.

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] Let $p$-comparable operations (resp., $p$-incomparable operations) be the set of operations with items whose priority is comparable with $p$ (resp., incomparable with $p$). It seems that we can construct $l''_1$, $l''_2$ and $l''_3$ as the projection of $l'$ into operations of $u$, $v$ and $w$, respectively. However, this is incorrect, since $\mathsf{MatchedMaxPriority}(l,x)$ has no restriction to $p$-incomparable operations operations in $u \cdot v$, and thus, there is no guarantee that the projection of $l'$ into $p$-incomparable operations operations in $u \cdot v$ being correct. In this example, such projection is $\textit{put}(z_1,p_3) \cdot \textit{rm}(z_2)$ and is incorrect.

@@

\item[-] The first step is to define $W'$. The $p$-comparable operations in $W'$ is same as that in $w$. To obtain $p$-incomparable operations in $W'$, we try to find a $p$-incomparable operation $o$ which either happens before some $p$-comparable operations in $w$, or with linearization points after $\textit{rm}(x)$. Then, we put $o$ and all $p$-incomparable operations after $o$ in $l'$ into $W'$ (emphasized by boxes in example). In this example, $o$ is $\textit{rm}(z_1)$, and $p$-incomparable operations after $o$ in $l'$ is $\textit{rm}(z_2)$, which are emphasized by adding boxes. In this process, whether a $p$-incomparable operation is in $W'$ or not only relies whether it is before or after $o$ in $l'$.
